%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper]{moderncv}


\usepackage{verbatim}
%\usepackage{hyperref}
% moderncv themes
\moderncvtheme[orange]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem
%\definecolor{darkblue}{HTML}{EAB988}
%\definecolor{darkblue}{HTML}{9C9F84}
%\definecolor{darkblue}{HTML}{A97D5D}
\definecolor{darkblue}{HTML}{405774}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths
% personal data
\firstname{Sanket}
\familyname{Parmar}
\address{Bangalore, India}{}    % optional, remove the line if not wanted
\mobile{+91 8860308444}                    % optional, remove the line if not wanted
\email{sanketsparmar@gmail.com}                      % optional, remove the line if not wanted
\homepage{sanketparmar.in}                % optional, remove the line if not wanted
% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
\AfterPreamble{
\hypersetup{colorlinks=true,urlcolor=darkblue,linkcolor=darkblue}
}
%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace{-40px}

\section{Summary}
%\vspace{-10px}
\cvline{}{
\begin{itemize}%
\item Skilled professional offering an experience of 4+ years in the embedded software and IT domain
\item Excellent analytical skill summed up with proficiency in C, Linux and Open source tools
\item Well adapted with agile development and open to work in multi cultural environment
\item Expert in debugging/problem solving for complex system
\item Advanced in Linux Kernel modules, Device driver development for STB,  Multimedia over IP
%\item Actively working on development and support of RF/IP frontend device driver at ST Microelectronics(subcon)
\end{itemize}
\vspace{-12px}
}

\section{Experience}
\cventry {2014--Present}{System Software Engineer}{NVIDIA (Smartplay Technologies)}{Bangalore}{} {
Part of Tegra system software group. Maintained and supported system software for Tegra based VCM.\\
}

\cventry{2012--2013}{System Software Engineer}{STMicroelectronics (SmartPlay Technologies)}{Noida}{}{
Worked with INPUTs subsystem team for set-top box at ST Microelectronics. Maintained and developed  RF/IP Frontend driver for STLinux.
Responsible for new hardware support, customer support, and maintenance. Also served as sub system integrator.\\
}

\cventry{2011--2012}{Intern}{ST Microelectronics}{Noida}{}
 {
Worked on audio driver of STB based chip sets. Maintained
different modules of audio driver. Implemented new features to validate different components of audio driver.\\
}

\cventry{2008--2010}{System Software Engineer}{Merce Technologies}{Mumbai, India}{}
{
Developed and supported different modules of Merce product.
Key member of mass mailing product {\em Broadside}. Deployed and maintain whole system setup at client sides.
}

\section{Education}
\cventry{2010--2012}{M.Tech Information and Communication Technology}{6.70 CPI}{}{}{Nirma University, Gujarat, India}
\cventry{2004--2008}{B.E Information Technology}{7.21 CPI}{}{}{GCET, Sardar Patel University, Gujarat, India}

\section{Projects}
\cventry{}{RF/IP Frontend device driver for STB}{ST Microelectronics}{}{}{
\vspace{1px}
\begin{itemize}
\item Worked on kernel space device driver for ST and other 3rd party  tuner and demodulator hardwares, IP frontend drive
\item Provided support for different tuners/demods for different broadcast transmission standards(dvbs, dvbc, dvbt)
\item Worked on multimedia over IP(IPFE) with UDP and RTP support
\item Improved IPFE performance using multithreading and FEC/Jitter related optimization
\item Made tools to provide easy debugging/statistical information
\item Used KDB, SYSFS, Oops analysis for debugging
\item Automated different development using Jenkins CI
\end{itemize}
\vspace{1px}}

\cventry{}{Audio device driver for STB}{ST Microelectronics}{}{}{
\vspace{1px}
\begin{itemize}
\item Developed and maintained audio device driver for STB on OS21 and Linux
\item Implemented new development request for different parts of audio device driver
\item Improved DDP parser for MS11 certification
\item Worked on CRC based verdict generation to test different components of audio driver
\item Automated firmware generation process
\end{itemize}
\vspace{1px}}

\cventry{}{Broadside}{Merce Technologies}{}{}{
\vspace{1px}
Broadside is an automated mass mailing solution. It provides different facilities
like bulk mail, mailing list, auto responder and MIS reports.
\begin{itemize}
\item Developed the logic and core code of the application
\item Implemented daemons to check the status of each transmitters, track the applications’ version
\item Implemented bounce mail handler with bounce mail parser
\item Implemented bulk uploader to upload the logs in postgres database
\item Integrated DKIM key and Sender policy Framework in broadside
\item Programmed the E-mail refile notification module which reminds the users
to keep the inbox size in allowable limit.
\item Implemented Password expiry module which allows admins to impose password expiry.
\item Maintenance and on-site support
\end{itemize}
\vspace{1px}}



\section{Masters thesis}
\cvline{Title}{\emph{Parallel I/O Performance Optimization Using Interval Based I/O}}
\cvline{Adviser}{Prof. Zunnun Narmawala, Nirma University, Ahmedabad}
\cvline{Description}{Propose a theoretical model which addresses the storage
problem of application data in parallel file systems legacy view. We develop
a new file model and required software infrastructure using MPI views and data layout awareness technique to distribute
the objects on I/O servers.}

\section{Computer skills}
\cvcomputer{Super}{C, Shell, Perl}{Good}{C++, Java, PHP, HTML}
\cvcomputer{Passable}{Python, Assembly, \LaTeX}{Platforms}{Linux, Android}
\cvcomputer{Tools}{Git, Vim, GDB, Photoshop, VirtualBox}{Database}{MySQL, PostgreSQL}

\section{Interests}
\cvcomputer{Software}{Linux, Android and Open Source}{Embedded}{Arduino, Raspberry Pi}
\cvcomputer{Domain}{Device Driver, Kernel Development}{Other}{\href{http://sanketparmar.in}{Blogging}, Photography}

\section{References}
\cvline{}{Available upon request}

\end{document}
